\section{The LASM Framework}
\label{sec:framework}

The Large-scale Adversarial Security Metric (LASM) framework is designed to bridge the severe theoretical gap between static, isolated model evaluation and dynamic, system-level enterprise deployment. Unlike existing paradigms that treat Generative AI components as standalone text prediction engines, LASM models the entire socio-technical system iteratively. To accomplish this, we formalize five continuously interacting components that collectively map technical exploitability, temporal decay, and game-theoretic deterrence.

\subsection{LLM Attack Surface (LAS)}
\label{subsec:las}

We first define the architectural exposure of the system. An LLM-based system is modeled as a heterogeneous directed graph $G = (V, E)$, where the vertices $V$ represent discrete processing nodes (e.g., the LLM orchestrator, a RAG retrieval engine, external API executors) and the edges $E$ map data flows carrying varying trust weights. Within this topology, we identify specific entry points ($EP$), encompassing System Prompts ($EP_{SP}$), User Prompts ($EP_{UP}$), and Agent Messages ($EP_{AM}$).

The LLM Attack Surface ($LAS$) quantifies the macroscopic vulnerability under a computational budget $B$ at deployment time $t$ for target system $S$:
\begin{equation}
    LAS(S, t, B) = \alpha \cdot \sum_{i \in EP} w_i(S) \cdot |E_i(S)| \cdot p_i(t, B) \cdot h_i
\end{equation}

Here, $w_i(S)$ denotes the architectural accessibility weight, prioritizing elements exposed to untrusted users. $|E_i(S)|$ represents the absolute count of entry vectors within the domain $i$. The term $p_i(t, B)$ is the empirical exploitation probability given the current attacker capabilities at time $t$ under querying budget $B$, while $h_i$ assigns a harm severity coefficient based on standardized taxonomies (e.g., MITRE ATLAS). 

Crucially, modern deployments are rarely isolated models. To account for autonomous tool usage and cascading downstream exploits, LASM introduces the \textbf{Integrational Composability Factor ($\alpha$)}. $\alpha$ acts as an exponential multiplier when $S$ operates as a multi-agent framework, proving that synergistic tool access expands the attack surface non-linearly.

\subsection{Standardized Attack Success Rate (SASR)}
\label{subsec:sasr}

Once the attack surface is mapped, we must accurately measure the discrete vulnerability. The prevailing metric, binary Attack Success Rate (ASR), is fundamentally flawed; it frequently succumbs to the \textit{False-Safety Paradigm}, granting passing scores to "illusionary safe" responses such as compliant gibberish or partial disclosures. 

To rectify this reporting bias, LASM introduces the Standardized Attack Success Rate (SASR), a continuous vulnerability metric computed over a standard adversarial prompt set $Q$ subject to a Normalized Query Unit (NQU) Budget $B$. To guarantee metric credibility, SASR employs a rigorous \textbf{Three-Judge Protocol (3JP)}:

\begin{enumerate}
    \item \textbf{Heuristic Classifier ($C_1$):} A rapid, rule-based classifier that filters out absolute, hard-coded safety refusals.
    \item \textbf{High-Capacity LLM Judge ($C_{LLM}$):} A frontier model (e.g., \texttt{Qwen2.5-3B}) instructed with specialized rubrics to continuously score the \textit{specificity}, \textit{convincingness}, and \textit{actionability} of the adversarial execution.
    \item \textbf{Human-in-the-Loop Validation:} A mandatory threshold ensuring inter-rater reliability via Cohen's Kappa ($k \ge 0.6$).
\end{enumerate}

For any given adversarial query $q \in Q$, the localized SASR is computed as:
\begin{equation}
    SASR_{q} = \frac{SR_{C_1}(q) + SR_{C_{LLM}}(q)}{2}
\end{equation}
By aggregating $SASR_q$ across $Q$, defenders extract a substantially more realistic penetration probability that resists naive evasions.

\subsection{Temporal Robustness Curve (TRC)}
\label{subsec:trc}

Security in Generative AI is not a static property but a continuously decaying state. As novel jailbreaking techniques (e.g., GCG, PAIR) are open-sourced, static filters degrade rapidly. LASM establishes the Temporal Robustness Curve (TRC) to forecast this degradation trajectory.

The TRC defines the effectiveness of a deployed defense mechanism $D$ against the mathematically strongest known adversarial attack algorithm $A^*$ at progressing time intervals $t$:
\begin{equation}
    TRC(D, t) = SASR(A^*(t), D, Q, B_{mid})
\end{equation}

By plotting this curve along intervals (e.g., $T_0$, $T_{+3}$, $T_{+6}$ months), we extract the \textbf{Defense Half-Life (DHL)}. The DHL is the strict chronological timeframe required for the system's baseline vulnerability ($SASR_{T_0}$) to double in magnitude, effectively breaching the enterprise risk threshold. This mandates a shift from point-in-time auditing to lifecycle forecasting.

\subsection{Game-Theoretic Extension: Economic Attack Surface (EAS)}
\label{subsec:eas}

In practice, high technical vulnerability (high LAS) rarely translates to guaranteed exploitation if the cost of the attack drastically outweighs the reward. LASM formalizes this deterrence by modeling the interaction as a Stackelberg Security Game between the system defender and distinct attacker profiles $\pi$ (e.g., script-kiddies vs. nation-state APTs).

A rational actor only proceeds if the Expected Gain $V_{target}$ exceeds their total expenditures. The Economic Attack Surface (EAS) acts as a mathematical restriction on the technical attack surface:
\begin{equation}
    EAS(S, t, B, \pi) = \sum_{i} LAS_i \cdot \mathbb{I} \Big[ V_{target} - (\delta \cdot C_{compute} + C_{opp}) > 0 \Big]
\end{equation}
where $\mathbb{I}$ is the indicator function. The term $C_{compute}$ denotes the cost per algorithmic iteration to bypass security, $C_{opp}$ models the profile's opportunity cost, and $\delta$ represents the system's Defense Multiplier (e.g., latency injection, rate-limiting, compute-heavy guardrails). The EAS elegantly proves that adversaries can be systematically deterred through economic friction, even if latent prompt-injection vulnerabilities technically remain.

\subsection{Attack Deterrence Threshold (ADT)}
\label{subsec:adt}

Building directly upon the EAS, defenders historically struggle with the \textit{over-defense problem}—stacking expensive, high-latency safety filters long after the threat model has been deterred. LASM provides a formal stopping criterion via the Attack Deterrence Threshold (ADT).

The ADT identifies the exact breakpoint for the optimal defense investment multiplier $\delta^*$:
\begin{equation}
    \delta^* = \frac{V_{target} - C_{opp}}{C_{compute}}
\end{equation}
When an enterprise scales their defense mechanism such that $\delta > \delta^*$, the Expected ROI for the adversary becomes mathematically negative. Under these conditions, the system secures an effective 0\% EAS with $100\%$ economic deterrence. The ADT ensures that security teams allocate resources rationally relative to their specific threat environment, establishing LASM as the foundation for modern enterprise AI security management.
